$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-02 paper/e6ssm-tuning-paper.tex
Removed tildes on U(1)_N charges to avoid potential confusion, especially since they should be unnecessary when ignoring U(1) mixing

H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big

@@

respectively and $\bar{g}^2=g_2^2+g'^2$. The charges $\tilde{Q}_1$,
$\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for

@@

\tilde{Q}_1v_1^2+\tilde{Q}_2v_2^2+\tilde{Q}_Ss^2\right
)\tilde{Q}_\phi.

@@

$|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq

@@

$U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance

@@

c(\theta,\tan\beta)&=1-\frac{4}{\left ( \tan^2\beta-1\right )}\frac{g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1-\tilde{Q}_2\tan^2\beta \right )\left ( \tilde{Q}_1\cos^2\beta+\tilde{Q}_2\sin^2\beta \right ),\label{eq:cdefn}\\
d(\theta,\tan\beta)&= \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tilde{Q}_S\left ( \tan^2\beta - 1\right )}.\label{eq:ddefn}

@@

\frac{\partial f_1}{\partial \tan\beta}&=&-\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\cos\beta+\sin\beta \left [ m_{H_d}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2\tilde{Q}_1\tilde{Q}_S \right )\right.\right.\nonumber\\
&&\left.\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}\tilde{Q}_1\tilde{Q}_2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_1^2\right )\right ]+3M_Z^2\,\sin^3\beta\left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\right.\nonumber\\
&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ]\right \},\nonumber\\
\frac{\partial f_1}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2\tilde{Q}_1\tilde{Q}_S\right )\,\cos\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin\beta \right ],\nonumber\\
\frac{\partial f_2}{\partial \tan\beta}&=&\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\sin\beta+\cos\beta\left [ m_{H_u}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2\tilde{Q}_2\tilde{Q}_S \right )\right.\right.\nonumber\\
&&\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}\tilde{Q}_1\tilde{Q}_2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2\right )\right ]+3M_Z^2\,\cos^3\beta \left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\nonumber\\
&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q}_2^2\right )\right ]\right \},\nonumber\\
\frac{\partial f_2}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2\tilde{Q}_2\tilde{Q}_S\right )\,\sin\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\cos\beta\right ],\nonumber\\
\frac{\partial f_3}{\partial \tan\beta}&=&\frac{2M_Z^2}{\bar{g}^2}\,\cos^2\beta\left [ g_1'^2\tilde{Q}_Ss\left ( \tilde{Q}_2-\tilde{Q}_1\right )\,\sin 2\beta-\sqrt{2}\lambda A_\lambda\,\cos 2\beta\right ],\nonumber\\
\frac{\partial f_3}{\partial s}&=&m_S^2+\frac{2\lambda^2M_Z^2}{\bar{g}^2}+\frac{g_1'^2}{2}\tilde{Q}_S\left [\frac{4M_Z^2}{\bar{g}^2}\left ( \tilde{Q}_1\,\cos^2\beta+\tilde{Q}_2\,\sin^2\beta\right ) +3\tilde{Q}_S s^2\right ].\nonumber

@@

\frac{\partial f_1}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\cos\beta\left ( m_{H_d}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_1\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_1^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\sin\beta\nonumber \\
&&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(\tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ],\nonumber\\
\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_2\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
&&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q_2}^2\right )\right ],\nonumber \\
\frac{\partial f_3}{\partial M_Z}&=&\frac{4M_Z}{\bar{g}^2}\left [ \lambda^2s-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin 2\beta+g_1'^2\tilde{Q}_Ss\left ( \tilde{Q}_1\,\cos^2\beta+\tilde{Q}_2\,\sin^2\beta \right )\right ].\nonumber

@@

\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{\tilde{Q}}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15

@@

\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{\tilde{Q}}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15

@@

\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}\\
\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(\tilde{Q}_{\bar{D}}^2+\tilde{Q}_D^2+\tilde{Q}_S^2\right)-30
   y_b^2 \left(\tilde{Q}_d^2+\tilde{Q}_1^2+\tilde{Q}_Q^2\right)+120 g_3^2 \Pi _{\tilde{Q}}^C\right.\nonumber \\

@@

   \left(\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_1^2\right)+15 g_2^2 \Pi _{\tilde{Q}}^L+10 g_1'^2 \Pi _{\tilde{Q}}+6
   g_1^2 \Pi _{\tilde{Q}}^Y\nonumber\\
&\quad\left.{}-10 \Sigma _{\lambda } \left(\tilde{Q}_S^2+\tilde{Q}_1^2+\tilde{Q}_2^2\right)-30 y_t^2
   \left(\tilde{Q}_u^2+\tilde{Q}_2^2+\tilde{Q}_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}

@@

\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta

@@

\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4\\

@@

\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2=\frac{1}{2}.

@@

b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{\tilde{Q}}^2.\label{eq:USSMg1pOt2Coeff}

@@

\beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( \tilde{Q}_1^2 + \tilde{Q}_2^2 + \tilde{Q}_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\

@@

&{}\left.+g_1'^2\left [ 4\tilde{Q}_S^2\lambda^2 -6\left ( \tilde{Q}_2^2-\tilde{Q}_Q^2-\tilde{Q}_u^2\right )y_t^2-6\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2-\tilde{Q}_d^2\right )y_b^2 \right.\right.\nonumber\\
&{}\left.-2\left ( \tilde{Q}_1^2-\tilde{Q}_L^2-\tilde{Q}_e^2\right )y_\tau^2-6\left ( \tilde{Q}_S^2-\tilde{Q}_D^2-\tilde{Q}_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( \tilde{Q}_S^2-\tilde{Q}_1^2-\tilde{Q}_2^2\right )\Sigma_\lambda\right ]\nonumber\\
&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2\tilde{Q}_1^4+2\tilde{Q}_2^4+2\tilde{Q}_S^4+\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Sigma_{\tilde{Q}}\right ]\nonumber\\
&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\

@@

&{}-2g_1'^2\left [ 4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2\right )\right .\nonumber\\
&{}+3y_b^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_d^2+\tilde{Q}_Q^2+\tilde{Q}_S^2 \right )+3y_t^2\left ( \tilde{Q}_1^2+2\tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_S^2+\tilde{Q}_u^2\right )\nonumber\\
&{}\left.+y_\tau^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
&{}+2g_1'^4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2-\Sigma_{\tilde{Q}}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\nonumber\\
&{}+\frac{6}{5}g_1^2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}

@@

\beta_{a_\lambda}^{(1)}&=2\lambda \left [ 2 \Sigma_{a_\lambda}+3\Sigma_{a_\kappa}+3y_ta_t+3y_ba_b+y_\tau a_\tau+\frac{3}{5}g_1^2M_1+3g_2^2 M_2+2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\right ]\nonumber\\
&{}+a_\lambda \left [ 6\lambda^2+2\Sigma_\lambda+3\Sigma_\kappa+3y_t^2+3y_b^2+y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\

@@

\Sigma_1'&=\sum_{i=1}^3\left ( 6\tilde{Q}_Qm_{Qi}^2+3\tilde{Q}_um_{ui}^2+3\tilde{Q}_dm_{di}^2+\tilde{Q}_em_{ei}^2+2\tilde{Q}_Lm_{Li}^2+2\tilde{Q}_2m_{H_{ui}}^2+2\tilde{Q}_1m_{H_{di}}^2\right.\nonumber\\
&\quad{}\left.+\tilde{Q}_Sm_{Si}^2+3\tilde{Q}_{\overline{D}}m_{\overline{D}_i}^2+3\tilde{Q}_Dm_{Di}^2\right )+2\tilde{Q}_{H'}m_{H'}^2+2\tilde{Q}_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}

@@

&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8\tilde{Q}_1^2g_1'^2 M_1'^2\nonumber\\
&{}-\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\

@@

&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8\tilde{Q}_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\

@@

&{}-8\tilde{Q}_S^2g_1'^2M_1'^2+2\tilde{Q}_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\

@@

\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
\beta_{y_t}^{(2)}&=,\label{eq:USSMYu22BetaTwoLoop}\\
b_{y_t}^{(2)}&=,\label{eq:USSMYu22Ot2Coeff}

>>>>

H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big

@@

respectively and $\bar{g}^2=g_2^2+g'^2$. The charges $Q_1$,
$Q_2$ and $Q_S$ are effective $U(1)'$ charges for

@@

Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right
)Q_\phi.

@@

$|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $Q_S\neq

@@

$U(1)$ extended models for which $Q_S\neq 0$, the importance

@@

c(\theta,\tan\beta)&=1-\frac{4}{\left ( \tan^2\beta-1\right )}\frac{g_1'^2}{\bar{g}^2}\left ( Q_1-Q_2\tan^2\beta \right )\left ( Q_1\cos^2\beta+Q_2\sin^2\beta \right ),\label{eq:cdefn}\\
d(\theta,\tan\beta)&= \frac{Q_1-Q_2\tan^2\beta}{Q_S\left ( \tan^2\beta - 1\right )}.\label{eq:ddefn}

@@

\frac{\partial f_1}{\partial \tan\beta}&=&-\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\cos\beta+\sin\beta \left [ m_{H_d}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2Q_1Q_S \right )\right.\right.\nonumber\\
&&\left.\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}Q_1Q_2+\frac{6g_1'^2}{\bar{g}^2}Q_1^2\right )\right ]+3M_Z^2\,\sin^3\beta\left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\right.\nonumber\\
&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( Q_1Q_2-Q_1^2\right )\right ]\right \},\nonumber\\
\frac{\partial f_1}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2Q_1Q_S\right )\,\cos\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin\beta \right ],\nonumber\\
\frac{\partial f_2}{\partial \tan\beta}&=&\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\sin\beta+\cos\beta\left [ m_{H_u}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2Q_2Q_S \right )\right.\right.\nonumber\\
&&\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}Q_1Q_2+\frac{6g_1'^2}{\bar{g}^2}Q_2^2\right )\right ]+3M_Z^2\,\cos^3\beta \left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\nonumber\\
&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( Q_1Q_2-Q_2^2\right )\right ]\right \},\nonumber\\
\frac{\partial f_2}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2Q_2Q_S\right )\,\sin\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\cos\beta\right ],\nonumber\\
\frac{\partial f_3}{\partial \tan\beta}&=&\frac{2M_Z^2}{\bar{g}^2}\,\cos^2\beta\left [ g_1'^2Q_Ss\left ( Q_2-Q_1\right )\,\sin 2\beta-\sqrt{2}\lambda A_\lambda\,\cos 2\beta\right ],\nonumber\\
\frac{\partial f_3}{\partial s}&=&m_S^2+\frac{2\lambda^2M_Z^2}{\bar{g}^2}+\frac{g_1'^2}{2}Q_S\left [\frac{4M_Z^2}{\bar{g}^2}\left ( Q_1\,\cos^2\beta+Q_2\,\sin^2\beta\right ) +3Q_S s^2\right ].\nonumber

@@

\frac{\partial f_1}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\cos\beta\left ( m_{H_d}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}Q_1Q_Ss^2+\frac{6g_1'^2}{\bar{g}^2}Q_1^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\sin\beta\nonumber \\
&&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(Q_1Q_2-Q_1^2\right )\right ],\nonumber\\
\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}Q_2Q_Ss^2+\frac{6g_1'^2}{\bar{g}^2}Q_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
&&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( Q_1Q_2-\tilde{Q_2}^2\right )\right ],\nonumber \\
\frac{\partial f_3}{\partial M_Z}&=&\frac{4M_Z}{\bar{g}^2}\left [ \lambda^2s-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin 2\beta+g_1'^2Q_Ss\left ( Q_1\,\cos^2\beta+Q_2\,\sin^2\beta \right )\right ].\nonumber

@@

\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{Q}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15

@@

\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{Q}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15

@@

\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{Q},\label{eq:USSMg1pBetaOneLoop}\\
\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(Q_{\bar{D}}^2+Q_D^2+Q_S^2\right)-30
   y_b^2 \left(Q_d^2+Q_1^2+Q_Q^2\right)+120 g_3^2 \Pi _{Q}^C\right.\nonumber \\

@@

   \left(Q_e^2+Q_L^2+Q_1^2\right)+15 g_2^2 \Pi _{Q}^L+10 g_1'^2 \Pi _{Q}+6
   g_1^2 \Pi _{Q}^Y\nonumber\\
&\quad\left.{}-10 \Sigma _{\lambda } \left(Q_S^2+Q_1^2+Q_2^2\right)-30 y_t^2
   \left(Q_u^2+Q_2^2+Q_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}

@@

\Sigma_{Q}=\sum_i Q_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta

@@

\Sigma_{Q}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^YQ_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
\Pi_{Q}&=\sum_i Q_i^4\\

@@

\Pi_{Q}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2Q_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
\Pi_{Q}^L&=3Q_1^2+3Q_2^2+Q_{H'}^2+Q_{\overline{H'}}^2+3Q_L^2+9Q_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
\Pi_{Q}^C&=Q_d^2+Q_D^2+Q_{\overline{D}}^2+2Q_Q^2+Q_u^2=\frac{1}{2}.

@@

b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{Q}^2.\label{eq:USSMg1pOt2Coeff}

@@

\beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\

@@

&{}\left.+g_1'^2\left [ 4Q_S^2\lambda^2 -6\left ( Q_2^2-Q_Q^2-Q_u^2\right )y_t^2-6\left ( Q_1^2-Q_Q^2-Q_d^2\right )y_b^2 \right.\right.\nonumber\\
&{}\left.-2\left ( Q_1^2-Q_L^2-Q_e^2\right )y_\tau^2-6\left ( Q_S^2-Q_D^2-Q_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( Q_S^2-Q_1^2-Q_2^2\right )\Sigma_\lambda\right ]\nonumber\\
&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2-Q_1\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\

@@

&{}-2g_1'^2\left [ 4\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( Q_1^2+Q_2^2+Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\right .\nonumber\\
&{}+3y_b^2\left ( 2Q_1^2+Q_2^2+Q_d^2+Q_Q^2+Q_S^2 \right )+3y_t^2\left ( Q_1^2+2Q_2^2+Q_Q^2+Q_S^2+Q_u^2\right )\nonumber\\
&{}\left.+y_\tau^2\left ( 2Q_1^2+Q_2^2+Q_e^2+Q_L^2+Q_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
&{}+2g_1'^4\left ( Q_1^2+Q_2^2+Q_S^2 \right )\left (Q_1^2+Q_2^2+Q_S^2-\Sigma_{Q}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\nonumber\\
&{}+\frac{6}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}

@@

\beta_{a_\lambda}^{(1)}&=a_\lambda \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right]\nonumber\\
&{}+\lambda \left [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\right.\nonumber\\
&{}\left.+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\

@@

\Sigma_1'&=\sum_{i=1}^3\left ( 6Q_Qm_{Qi}^2+3Q_um_{ui}^2+3Q_dm_{di}^2+Q_em_{ei}^2+2Q_Lm_{Li}^2+2Q_2m_{H_{ui}}^2+2Q_1m_{H_{di}}^2\right.\nonumber\\
&\quad{}\left.+Q_Sm_{Si}^2+3Q_{\overline{D}}m_{\overline{D}_i}^2+3Q_Dm_{Di}^2\right )+2Q_{H'}m_{H'}^2+2Q_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}

@@

&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8Q_1^2g_1'^2 M_1'^2\nonumber\\
&{}-\frac{3}{5}g_1^2\Sigma_1+2Q_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\

@@

&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8Q_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2Q_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\

@@

&{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\

@@

\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
\beta_{y_t}^{(2)}&=y_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
&{}+2g_1'^2\left [ \lambda^2\left ( Q_1^2-Q_2^2+Q_S^2 \right )+2y_t^2\left ( 2Q_Q^2+Q_u^2\right )+y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\right ]\nonumber\\
&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
&{}+2g_1'^4\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
